\section{Introduction}\label{chap:introduction}


The online travel accommodation market is a dynamic and fiercely competitive landscape. Launching a new booking aggregator, particularly in a big touristic city like Rio de Janeiro, Brazil, presents formidable challenges. Foremost among these is the `cold start problem': in the absence of historical user data --- such as bookings, reviews, or behavioral patterns --- the platform struggles to meaningfully rank listings or offer relevant recommendations. This initial lack of personalization can lead to a frustrating user experience, discouraging engagement and critically hampering the platform's early growth and market penetration.

To effectively address this critical issue, we propose an innovative, data-driven solution. This project leverages publicly available Airbnb data for the Rio de Janeiro region to build a predictive model. Our core objective is to accurately estimate review scores for our new, unrated listings based purely on their intrinsic features --- location, price, amenities, host attributes and others. These predicted scores will then serve as a foundational element for platform's initial ranking algorithms, enabling business to surface high-quality accommodations, enhance discoverability, and immediately improve the user journey.

This initiative directly aligns our technical capabilities with key business objectives: effectively solve the cold start problem, increase booking conversion rates from launch, and accelerate revenue generation in the early stages. In the following sections of this report, we will delve into a specific business context, examine the data structure, and take a detailed look at our methodology for developing a reliable forecasting system designed to function successfully even under the constraints of launching a new platform.
